---
title: "Lab 01 - Hello R"
author: "Holland Sun"
date: "2026 Jan 16"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE,warning=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```
***Note: add **warning=FALSE** to avoid warning sentence***


## Exercises

### Exercise 1

datasaurus_dozen has 1846 rows and 3 variables(I think that is columns),and the 3 variables: 

* **dataset**: which refers to which dataset the data are from

* **x**: which refers to the x-values

* **y**: which refers to the y-values

### Exercise 2

First, filter the **dino** dataset, and then use **ggplpt** to visualization:

```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, calculate the correlation of x and y:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```



### Exercise 3
Use the similar code we do the same thing on **star** dataset
First, filter the **star** dataset, and then use **ggplpt** to visualization:

```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Second, calculate the **r** of **star** dataset

```{r cor-star, fig.height=5, fig.width=5}
star_data %>%
  summarize(r = cor(x, y))
```

the correlation coefficient of **star** dataset is **-0.0630** which is ***smaller*** than the **-0.0645** of **dino** dataset.

*( For **smaller**, I mean the strength of correlation, not the number itself )*

### Exercise 4

Again, use the similar code we do the same thing on **circle** dataset
First, filter the **circle** dataset, and then use **ggplpt** to visualization:

```{r plot-circle, fig.height=5, fig.width=5}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Second, calculate the **r** of **circle** dataset
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
the correlation coefficient of **circle** dataset is **-0.0683** which is ***larger*** than the **-0.0645** of **dino** dataset.

*( Again, For **larger**, I mean the strength of correlation, not the number itself )*

### Exercise 5

Finally We use the similar code to plot all those **13** dataset:

```{r plot-alldataset, fig.height=14, fig.width=10}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

Second, calculate  **r** of all **13** datasets.
To know better the **strength** of these 13 **r**, maybe we can then transit the **r** into **arrange** function to help us,So i make some changes on the original codes:
```{r cor-alldataset}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))%>%
  arrange(desc(abs(r)))
```
 
### Exercise 6 (maybe)
 adjust the size of figure and other stuffs.
 🎉 bravo!!! Holland made it
 
