---
title: "Lab 01 - Hello R"
author: "Holland Sun"
date: "2026 Jan 16"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

datasaurus_dozen has 1846 rows and 3 variables(I think that is columns),and the 3 variables: 

* **dataset**: which refers to which dataset the data are from

* **x**: which refers to the x-values

* **y**: which refers to the y-values

### Exercise 2

First, filter the **dino** dataset, and then use **ggplpt** to visualization:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, calculate the correlation of x and y:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```



### Exercise 3
Use the samiliar code we do the same thing on **star** dataset
First, filter the **star** dataset, and then use **ggplpt** to visualization:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Second, calculate the **r** of **star** dataset

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

the correlation coefficient of **star** dataset is **-0.0630** which is smaller than the **-0.0645** of **dino** dataset.

*(For **smaller**, I mean the strenth of correlation not the number).*

### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}

```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far. Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!
